It is my great pleasure to welcome all of you to attend the
31\textsuperscript{st} New England Statistics Symposium.  On behalf of
the Department of Statistics at the University of Connecticut, I would
like to wish all the delegates of the 31st New England Statistics
Symposium (NESS) an enjoyable visit to our department and the
campus. We are thrilled to have this year two distinguished keynote
speakers: Professor Xihong Lin of Harvard School of Public Health and
Professor David Madigan of Columbia University. I would also like to
thank Professor Douglas Bates, Mr. Jared Huling, and Professor
Menggang Yu of University of Wisconsin–Madison and Professors Kun Chen
and Robert Aseltine of University of Connecticut for offering three
short courses on Friday, April 21, 2017.

My sincere thanks go to the leadership of Professors Haim Bar, Kun
Chen, Jun Yan (Chair) and Yuping Zhang for organizing this
symposium. I would like to acknowledge Haim for taking over the chair
role since Jun’s medical leave.  I further thank Ms. Megan Petsa,
Ms. Tracy Burke, Henry Linder, Hannah Melroy, Gregory Vaughan, and
many other graduate student volunteers for their help at each stage of
the planning for this symposium. I am confident that the scientific
program for this symposium will be of high quality and lead to dynamic
exchange of ideas and fruitful interactions between the statistical
scientists and graduate students throughout New England and beyond.

I would like to take this opportunity to acknowledge our generous
sponsors: College of Liberal Arts \& Sciences Dean’s Office, UConn
Department of Statistics, Connecticut Chapter of the American
Statistical Association, IBM T.J. Watson Research Center, Liberty
Mutual, Pfizer Inc., The Hartford, and Travelers Insurance Company. I
would like to thank the IBM T.J. Watson Research Center and Liberty
Mutual for sponsoring the Student Awards at the 31\textsuperscript{st} NESS.

Finally, I would like to invite all of you to celebrate the
establishment of the New England Statistical Society. Thanks to
Xiao-Li Meng, Kun Chen, coordinators and members of the society task
force groups for their great effort. Also thanks to the faculty of
UConn Department of Statistics for their tremendous support.

Welcome to UConn and Storrs.

With best wishes,

\textbf{Ming-Hui Chen} \\
Professor and Head, Department of Statistics \\
University of Connecticut \\[1em]

\newpage

Welcome to the University of Connecticut!  I amm delighted that UConn is
hosting this conference on its 30th anniversary.  We are proud of our
Statistics department and honored by this opportunity to host
statisticians from across New England and provide a forum for them to
discuss emerging issues, share research expertise, and meet old
friends.

I’d like to particularly thank the Symposium’s local hosts and
organizers from UConn, Drs. Jun Yan, Haim Bar, Kun Chen, and Yuping
Zhang, for their efforts in pulling this meeting together. \\[1em]

\textbf{Jeremy Teitelbaum} \\
Interim Provost \& Executive Vice President for Academic Affairs \\
University of Connecticut \\[1em]

\hrulefill

{\centering
  \subsection*{NESS Organizing Committee}

  Haim Bar, Kun Chen, Jun Yan (Chair), Yuping Zhang

}

