---
title: NESS registration and abstract submission summary
author: Henry Linder (mhlinder@gmail.com)
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    template: ~/links/defaults/rmd/mhl.tex
---

# Setup

```{r, message = FALSE, error = FALSE}
library(magrittr)
library(dplyr)

library(readr)

abs <-
    read_csv("../bak/abstracts.csv")
reg <-
    read_csv("../bak/reg.csv")

```

# Abstracts submitted without a registration

```{r}
regnums <- abs$reg %>% gsub("[\t ]", "", .)

ix_missing <- which((regnums == "NESS17-1234") |
                    (!regnums %in% reg$invoice))

abs[ix_missing,]$presenter
```

# Speakers without an abstract

Load data parsed from files:

* Invited sessions schedule and program
* Submitted abstracts
* Registration

We generate a data frame with rows representing an individual speaker.

```{r}

load("../parsed.Rdata")

df_sessions <-
    lapply(sessions,
       function(x) {
           inspkrs <- x$speakers
           outspkrs <- list()
           for (i in 1:length(inspkrs)) {
               s <- inspkrs[[i]]
               outspkrs[[i]] <- data.frame(name        = ifelse(is.null(s$name), NA, s$name),
                                           affiliation = ifelse(is.null(s$affiliation), NA, s$affiliation),
                                           paper       = ifelse(is.null(s$paper), NA, s$paper),
                                           session     = x$title,
                                           stringsAsFactors = FALSE)
           }
           do.call(bind_rows, outspkrs)
       }) %>%
    do.call(bind_rows, .)
```

Then we find the closest match to each row along three different
fields in the submitted abstracts:

* Presenter name
* Affiliation
* Paper title

```{r, results = 'asis'}

titles <- sapply(sessions, . %>% use_series(title))

df_sessions[c("ix_presenter", "ix_aff", "ix_title")] <- NA
for (i in 1:nrow(df_sessions)) {
## for (i in 1:1) {
    r <- df_sessions[i,]
    ix_session <- stringdist(r$session, abs$session) %>% which.min
    this_session <- abs$session[ix_session]
    candidates <- abs %>% filter(session == this_session)
    df_sessions$ix_presenter[i] <- stringdist(r$name, candidates$presenter) %>% which.min

    if (!is.na(r$affiliation))
        df_sessions$ix_aff[i] <- stringdist(r$affiliation, candidates$affiliation) %>% which.min
    if (!is.na(r$paper))
        df_sessions$ix_title[i] <- stringdist(r$paper, candidates$title) %>% which.min

    r <- df_sessions[i,]

    cat("\n")
    cat(sprintf("# %s\n", r$session))

    cat("\n")

    cat(sprintf("**%s**, %s: %s\n\n",
                  r$name,
                  r$affiliation,
                  r$paper))

    out_presenter <- sprintf("**%s**, %s: %s",
                             candidates$presenter[r$ix_presenter],
                             candidates$affiliation[r$ix_presenter],
                             candidates$title[r$ix_presenter])
    cat(sprintf("* %s\n (matched by presenter)\n", out_presenter))

    out_aff <- sprintf("**%s**, %s: %s",
                       candidates$presenter[r$ix_aff],
                       candidates$affiliation[r$ix_aff],
                       candidates$title[r$ix_aff])
    cat(sprintf("* %s\n (matched by affiliation)\n", out_aff))

    if (!is.na(r$ix_title)) {
        out_title <- sprintf("**%s**, %s: %s",
                             candidates$presenter[r$ix_title],
                             candidates$affiliation[r$ix_title],
                             candidates$title[r$ix_title])
        cat(sprintf("* %s\n (matched by title)\n", out_title))
    }

    cat("\n")
    cat("-----\n")
    cat("\n\n")

}

```

